A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
Edit result 5

    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
    optical colors of massive galaxies vary with radius. 
    We also study whether or these radial trends differ between our various samples. 
    These quantities contain interesting information about the physical processes that 
    shape galaxies, but here we study them mainly with two goals in mind:

        \item To see whether the ellipticity profile depends strongly on environment, 
            and to see whether or not the fact that we use an using average isophotal 
            shape for our our 1-D \mden{} profiles has any impact on our results.

        \item To verify that the average color gradient does not depend strongly on 
            the environment and that is not steep enough to cause a problem with our 
            choice the assumption that it is reasonable to use average \m2l for 
            comparing massive galaxies. 
            We extract color profiles by applying the isophotes in $i$-band to images 
            in other bands in ``forced photometry'' manner.

    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
    (this is the range where we can safely ignore differences in sky subtraction and 
    seeing across different bands). 
    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color}. 
    We also compare our results with previous work based on stacking SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

    We find that in general, the ellipticities of massive galaxies increases with 
    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    profiles are very similar.  
    This further hints that massive central galaxies in different halos but with 
    similar ``in-situ'' mass may experience different late-time merging histories. 
    Overall, the relative low ellipticity value and the fact that the ellipticity 
    gradients are shallow lead us to conclude that the use of an average 
    isophotal ellipticity is fine for this present study.

    Previous attempts to constrain ellipticity gradients have relied on image 
    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
    Compared to our measurements, we find that stacked ellipticity profiles tend to 
    underestimate the ellipticity in the outskirt. 
    Ellipticity profiles contain additional information about the assembly histories 
    and in future work, it would be of interest to compare our ellipticity profiles 
    with predictions from hydrodynamic simulations such as Illustris 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    (\citealt{Dubois2014}).

    In terms of color gradients, we find shallow and negative gradients of median 
    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
    in their median color profiles, which supports the assumption of using single 
    average \m2l{} value to estimate \mden{} profiles.
    The median $g-r$ color profiles are quite consistent with those based on 
    stacked SDSS images. 
    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
    however, it is important to point out that the SDSS $i$-band suffers from the 
    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
    could make the SDSS color appears redder. 
    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
    CCDs), therefore can help provide more accurate color estimates.
%% ------------------------------------------------------------------------------------ %%

>>>>

    In Paper~1, we show that the ellipticity of outer stellar halo in massive galaxy 
    steadily increases with \mtot{}, while the rest--frame color gradients do not show 
    clear \mtot{}-dependence. 
    Both these results provide us more insights about the assembly of massive galaxies. 
    Here we quickly look into the environment dependence of ellipticity and 
    rest--frame color profiles (Figure~\ref{fig:ell_color}).

    We focus on ellipticity and color profiles within 5--60 kpc where we can safely 
    ignore differences in sky subtraction and seeing across different bands. 
    We apply Galactic extinction and $k$-correction to both $(g-r)$ and $(g-i)$ color 
    profiles.
    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color} along with comparisons with previous 
    works based on stacked SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

    These results show:

        \item Once matched at fixed \mtot{}, the \rbcg{} and \nbcg{} galaxies 
            show similar average ellipticity profiles. 
            There is hint that suggests the central galaxies from more massive 
            haloes become slightly more elongated at $R>50$ kpc than the ones 
            in less massive halos with similar \mtot{}. 
            However, the uncertainties in the current profiles make it not 
            conclusive.

        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
            The average ellipticities in the inner region are very similar. 
            This further suggests that the more elongated outer stellar haloes 
            of massive halos relate to the accreted stars.

        \item For the rest--frame color gradients, we find shallow and negative 
            gradients for both \rbcg{} and \nbcg{} galaxies using both colors.
            We find no significant difference for both the \mtot{}- and 
            \minn{}--matched samples within 60 kpc.

    Besides these conclusions, these comparisons also suggest:

        \item The smooth ellipticity profile and its shallow gradient supports 
            the idea of using the flux-weighted average isophotal shape to 
            extract 1-D profiles of massive galaxies.

        \item The similarity of average rest-frame color profiles between the 
            \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
            single average \m2l{} will not bias our comparisons.
